An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-15 EconGrowth.Rnw
Now creating a graph of alpha, beta, gamma, and SSE vs. gamma. Looks good except for the text scaling for the axis labels and scales.

The Cobb-Douglas with energy parameter estimation process is challenging. To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$. Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\lambda$, $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$). The minimum $SSE$ occurs at a discontinuity caused by the constraint $\beta \geq 0.0$. The parameter estimation algorithm has difficulty recognizing the values of $\gamma$, $\alpha$, $\beta$, and $\lambda$ that produce minimum $SSE$, because the constrained model behaves very differently on either side of the discontinuity.

<<CDeGammaGraphsZA, fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
cdeGridGraphs("ZA", "Q")
@

>>>>

The Cobb-Douglas with energy parameter estimation process is challenging. To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$. Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$). The minimum $SSE$ occurs at a discontinuity caused by the constraint $\beta \geq 0.0$. The parameter estimation algorithm has difficulty recognizing the values of $\gamma$, $\alpha$, $\beta$, and $\lambda$ that produce minimum $SSE$, because the constrained model behaves very differently on either side of the discontinuity.

******** Fix the right y axis label. SSE should be italicized. *************

<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
cdeGridGraph("ZA", "Q")
@

### 2013-03-15 EconGrowthSeminar.Rnw
Now creating a graph of alpha, beta, gamma, and SSE vs. gamma. Looks good except for the text scaling for the axis labels and scales.

\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
<<CDeGammaGraphsZA>>=
  cdeGridGraphs("ZA", "Q")
@
\end{frame}

>>>>

\begin{frame}{Example Cobb-Douglas With Energy Fit} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
  cdeGridGraph("ZA", "Q", textScaling=0.8)
@
\end{frame}
